Estimating the number of clusters using Cross Validation

### 2015-06-19 cvclust.tex
typos

Now, ensure that $M$ large enough so that
\[
  4 \int_{\|x\| \geq 2M} \|x\|^2 P(dx) < \varepsilon.
\]
We will now show that if $A \in \sC_k \setminus \sE_k$, then $W(A,P) > W(B,P)
\geq m_{k}(P)$, which ensures that $W(\cdot, P)$ does not attain its infimum
over $\sA_k$ outside of $\sE_k$.  To see that this holds, suppose that $A$ is
any set $\sC_k \setminus \sE_k$.  This set has at least one point, $a_1$, in
$B(M)$, and at least one point outside $B(5M)$.  Consider thet set $A^\ast$
formed by removing all points of $A$ outside $B(5M)$.  Any point $x$ closer to
a cluster center outisde $B(5M)$ than to $a_1$ must satisfy $\|x\| \geq 2M$.
Thus,
\begin{align*}
  W(A^\ast, P)
    &\leq W(A,P) + \int_{\|x\| \geq 2M} \|x - a_1\|^2 P(dx) \\
    &\leq W(A,P) + \int_{\|x\| \geq 2M} (\|x\| + \|a_1\|)^2 P(dx) \\
    &\leq W(A,P) + 4 \int_{\|x\| \geq 2M} \|x\|^2 P(dx) \\
    &< W(A,P) + \varepsilon.
\end{align*}
Since $A^\ast$ has $k-1$ or fewer points, it must satisfy $W(A^\ast, P) \geq
m_{k-1}(P)$, so that $W(A, P) > m_{k-1}(P) - \varepsilon > W(B, P)$.

>>>>

Now, ensure that $M$ large enough so that
\[
  4 \int_{\|x\| \geq 2M} \|x\|^2 P(dx) < \varepsilon.
\]
We will now show that if $A \in \sC_k \setminus \sE_k$, then $W(A,P) > W(B,P)
\geq m_{k}(P)$, which ensures that $W(\cdot, P)$ does not attain its infimum
over $\sA_k$ outside of $\sE_k$.  To see that this holds, suppose that $A$ is
any set $\sC_k \setminus \sE_k$.  This set has at least one point, $a_1$, in
$B(M)$, and at least one point outside $B(5M)$.  Consider the set $A^\ast$
formed by removing all points of $A$ outside $B(5M)$.  Any point $x$ closer to
a cluster center outside $B(5M)$ than to $a_1$ must satisfy $\|x\| \geq 2M$.
Thus,
\begin{align*}
  W(A^\ast, P)
    &\leq W(A,P) + \int_{\|x\| \geq 2M} \|x - a_1\|^2 P(dx) \\
    &\leq W(A,P) + \int_{\|x\| \geq 2M} (\|x\| + \|a_1\|)^2 P(dx) \\
    &\leq W(A,P) + 4 \int_{\|x\| \geq 2M} \|x\|^2 P(dx) \\
    &< W(A,P) + \varepsilon.
\end{align*}
Since $A^\ast$ has $k-1$ or fewer points, it must satisfy $W(A^\ast, P) \geq
m_{k-1}(P)$, so that $W(A, P) > m_{k-1}(P) - \varepsilon > W(B, P)$.
